\noindent 
\textbf{ABSTRACT: } The abstract is a summary of your research project and includes motivation, aims, methods used, (preliminary) findings and (preliminary) conclusions.  The abstract should be a stand-alone document that someone could read to get a general overview of your research project.  

Write the abstract the font shown but make sure it is no longer than about 500 words (and it must fit on a single page which includes the title, authors and keywords). The words of ‘Abstract’ and ‘Keywords’ are set in bold and full caps.  Make sure you put your correct project code in the footer. If you have two supervisors you can list both of them.  If one of them is from industry you should give their company name etc.
Please note the following rules regarding the final paper:
\begin{itemize}
    \item First page (starts with - Title, Authors, Abstract(s) and Keywords) [MANDATORY] and then follows
    \item Body of the paper (text and tables and or figures in the format shown) [MANDATORY]
    \item Notation [OPTIONAL]
    \item Appendices [OPTIONAL]
    \item References [MANDATORY]
\end{itemize}

The total length of the paper is to be no more than \textbf{14pp for 3rdyr and 19pp for 4thyr}. A cover sheet is also required in addition to the research paper. Note that the cover sheet is not included in the page limit.
\\

\noindent 
\textbf{KEYWORDS:} Keyword 1, Keyword 2 and Keyword 3. You can include a maximum of 6 keywords for indexing purposes (spaced by commas). Keywords are single words or short phrases describing the main concepts/topics covered in the paper. Sometimes only 2 or 3 keywords will suffice, but definitely no more than six.
\\

\noindent 
\textbf{STATEMENT OF ORIGINALITY:} Using no more than 8 lines of text (including this one) please give your statement of what is original in this paper. E.g., ‘In this paper a new spreadsheet model is developed to calculate the settlement of foundations making use of previously published methods given by Meyerhof’.